{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2017-01-06 proposal/overview.tex
write about education implementation
undo easter egg in overview; it'll be in yield block discussion instead

\subsection{Pebbles}

@@

\subsubsection{P3}
In P3, students implement a kernel which provides the same system calls shown in Table~\ref{tab:syscalls}, previously provided by the reference kernel.
Although the internal interfaces are not mandated like they were in P2, all Pebbles kernels must necessarily contain the same abstract components. These include:
\begin{itemize}
	\item A round-robin scheduler, including context switching, timer handling, and runqueue management;
	\item Some approach to locking, often analogous to P2's concurrency primitives (henceforth referred to as ``kernel mutexes''), 
		and some approach to blocking threads indefinitely;
	\item A virtual memory implementation, including a program loader;
	\item Lifecycle management code for creation and destruction of kernel threads and processes;
	\item Other miscellany such as a suite of fault handlers to ensure no user program can cause the kernel itself to crash.
\end{itemize}
Because any combination of system calls or fault handlers can be invoked by user programs simultaneously,
concurrency bugs can arise from the interaction of any subset of kernel components with each other.
The most common bugs studence face arise from the interaction of some component with itself (e.g., concurrent invocations of {\tt new\_pages}/{\tt remove\_pages} in the same process),
or from the interaction between an exiting thread and some other thread trying to communicate with it ({\tt vanish} versus, well, anything else, really).
The most difficult concurrency problem in P3 is that of coordinating a parent and a child task that simultaneously exit:
when a task completes, live children and exited zombies must be handed off to the task's parent or to the {\tt init} process,
when the task's parent may itself be exiting;
meanwhile, threads in tasks that receive new children may need to be awakened from {\tt wait}.
Careless solutions to this problem are prone to data races or deadlocks.

>>>>

\subsection{Pebbles}
\label{sec:pebbles}

@@

\subsubsection{P3}
In P3, students implement a kernel which provides the same system calls shown in Table~\ref{tab:syscalls}, previously provided by the reference kernel.
Although the internal interfaces are not mandated like they were in P2, all Pebbles kernels must necessarily contain the same abstract components. These include:
\begin{itemize}
	\item A round-robin scheduler, including context switching, timer handling, and runqueue management;
	\item Some approach to locking, often analogous to P2's concurrency primitives (henceforth referred to as ``kernel mutexes''), 
	 ll       and some approach to blocking threads indefinitely;
	\item A virtual memory implementation, including a program loader;
	\item Lifecycle management code for creation and destruction of kernel threads and processes;
	\item Other miscellany such as a suite of fault handlers to ensure no user program can cause the kernel itself to crash.
\end{itemize}
Because any combination of system calls or fault handlers can be invoked by user programs simultaneously,
concurrency bugs can arise from the interaction of any subset of kernel components with each other.
The most common bugs studence face arise from the interaction of some component with itself (e.g., concurrent invocations of {\tt new\_pages}/{\tt remove\_pages} in the same process),
or from the interaction between an exiting thread and some other thread trying to communicate with it ({\tt vanish} versus, well, anything else, really).
The most difficult concurrency problem in P3 is that of coordinating a parent and a child task that simultaneously exit:
when a task completes, live children and exited zombies must be handed off to the task's parent or to the {\tt init} process,
when the task's parent may itself be exiting;
meanwhile, threads in tasks that receive new children may need to be awakened from {\tt wait}.
Careless solutions to this problem are prone to data races or deadlocks.

% TODO: Talk about the hurdle (both for p2 and p3).
